Pillar 1 - Sequential Pattern Mining

### 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
filter AR after apriori

```{r TODO}
# TODO: compute corrected confidence for AR
# TODO: support of AR_TFP
```

@@

###Computing probabilities
```{r}

@@

rm(n_students)
```

@@

#
# Making sequences
sequences     <- make_sequence(item = item   )
sequences_PF  <- make_sequence(item = item_PF)
sequences_HL  <- make_sequence(item = item_HL)
#sequences_TNT <- make_sequence(data = d_transactions_not_taken, item = item_TNT) # compute ad hoc
#sequences_TPF <- make_sequence(data = d_transactions_not_taken, item = item_TPF) # compute ad hoc
sequences_G   <- make_sequence(data = d_transactions_grade    , item = item_G  )

@@

my_apriori <- function(data, appearance){

@@

      # Chosen parameters
      parameter = list(
        supp = 0,    # min support
        smax = 1,    # max support
        conf = 0,    # min confidence
        minlen = 2,  # min length of 
        maxlen = 2,  # max length of rule
        ext = TRUE
        ),

      # impose restriction on lhs and rhs
      appearance = appearance,

@@

  AR %>%
    mutate_at(
      c("support", "lhs.support", 
        "confidence", "rhs.support",
        "lift"
        ),
      funs(round(., 5))
    ) %>%
    select(
      lhs, rhs,
      support, count, lhs.support,
      confidence, rhs.support,
      lift
    ) %>%
    arrange(
      desc(count)
    )

@@

```{r make_AR}
make_AR <- function(data, appearance = NULL,
                    data_support, type_rule){

  data %>%
    my_apriori(appearance = appearance) %>%
    clean_AR %>%
    compute_metrics(
      data_support = data_support,
      type_rule = !!enquo(type_rule)
      ) %>%
    editing_AR

@@

#
# AR fail
AR_PF <- transactions_PF %>%
  make_AR(

    # impose lhs and rhs to be fail
    appearance = list(
      both = d_transactions %>%
        filter(PF == "fail") %>%
        distinct(item_PF) %>%
        pull
    ),

    data_support = d_support,
    type_rule = rate.fail
  )

#
# AR low
AR_HL <- transactions_HL %>%
  make_AR(

    # impose lhs and rhs to be low
    appearance = list(
      both = d_transactions %>%
        filter(HL == "low") %>%
        distinct(`item_HL`) %>%
        pull
    ),

    data_support = d_support,
    type_rule = rate.low
  )

@@

AR_TPF <- transactions_TPF %>%
  make_AR(

    # impose lhs and rhs to be not taken
    appearance = list(
      rhs = d_transactions_TNT %>%
        filter(TPF == "fail") %>%
        distinct(`item_TPF`) %>%
        pull
    ),

    data_support = d_support_take,
    type_rule = rate.not
  )

@@

We save and remove objects:
```{r saving and rm}
#
# Save association rules
save(AR_taken, AR_PF, AR_HL, AR_TNT, AR_TPF, AR_G,
     file = "App/AR.RDATA")

# Remove objects
rm(clean_AR, my_apriori,
   transactions, transactions_PF, transactions_HL, transactions_G,
   AR_taken, AR_PF, AR_HL, AR_TNT, AR_G)
```

@@

```{r function clean SR}
# Transform rules from ruleInduction into a readable data frame
n_students <- length(unique(d_transactions$sequenceID))

>>>>

```{r TODO}
# TODO: corrected confidence for AR
```

@@

### Computing Support
```{r}

@@

@@

#
# Making sequences
sequences     <- make_sequence(item = item   )
sequences_PF  <- make_sequence(item = item_PF)
sequences_HL  <- make_sequence(item = item_HL)
#sequences_TNT <- make_sequence(data = d_transactions_not_taken, item = item_TNT) # compute ad hoc
#sequences_TPF <- make_sequence(data = d_transactions_not_taken, item = item_TPF) # compute ad hoc
sequences_G   <- make_sequence(data = d_transactions_G    , item = item_G  )

@@

my_apriori <- function(data){

@@

      # Chosen parameters
      parameter = list(
        supp = 0,    # min support
        smax = 1,    # max support
        conf = 0,    # min confidence
        minlen = 2,  # min length of 
        maxlen = 2  # max length of rule
        ),

@@

  AR %>%
    mutate_at(
      c("support", 
        "confidence", "rhs.support",
        "lift"
        ),
      funs(round(., 5))
    ) %>%
    select(
      lhs, rhs,
      support, count,
      confidence, rhs.support,
      lift
    ) %>%
    arrange(
      desc(count)
    )

@@

```{r make_AR}
make_AR <- function(data,
                    data_support, type_rule){

  data %>%
    my_apriori %>%
    clean_AR %>%
    compute_metrics(
      data_support = data_support,
      type_rule = !!enquo(type_rule)
      ) %>%
    editing_AR

@@

#
# AR fail
AR_PF <- transactions_PF %>%
  make_AR(
    data_support = d_support,
    type_rule = rate.fail
    ) %>%

  # lhs and rhs must be fail
  filter(
    str_detect(lhs, "fail"),
    str_detect(rhs, "fail")
    )

#
# AR low
AR_HL <- transactions_HL %>%
  make_AR(
    data_support = d_support,
    type_rule = rate.low
    ) %>%

    # lhs and rhs must be low
  filter(
    str_detect(lhs, "low"),
    str_detect(rhs, "low")
    )

@@

AR_TPF <- transactions_TPF %>%
  make_AR(
    data_support = d_support_take, 
    type_rule = rate.take
  ) %>%

  # lhs and rhs must be low
  filter(
    str_detect(rhs, "fail")
    )

rm(transactions, transactions_PF, transactions_HL, transactions_TPF)
```

@@

rm(d_support_grade, transactions_G)
```

We save and remove objects:
```{r saving and rm}
#
# Save association rules
save(AR_taken, AR_PF, AR_HL, AR_TPF, AR_G,
     file = "App/AR.RDATA")

# Remove objects
rm(my_apriori, clean_AR, compute_metrics, make_AR,
   AR_taken, AR_PF, AR_HL, AR_TPF, AR_G)
```

@@

```{r function clean SR}
# Transform rules from ruleInduction into a readable data frame
